MSE and dynamic state variable model with sigma function

### 2017-12-20 doc/previous versions/MSE_DEC.tex
changes scenarios MP

\abstract{
TBD
Farcas 2016:The case of fisheries management illustrates how the inherent structural instability of ecosystems can have deep-running policy implications. We contrast three types of management plans to achieve maximum sustainable yields (MSY) from multiple stocks and compare their effectiveness based on a management strategy evaluation (MSE) that uses complex food webs in its operating model. 
Use DSVM with a tuning parameter that measures how important is to be near optimal.
We use this DSVM to investigate how fishing locations change in response when fish biology is incorporated.}

@@

\keywords{word1; word2; word3; and word4}

@@

MSE involves building a simulation model for the entire process under study, complex enough both to address the current knowledge and uncertainty on the dynamics of fish stocks under fishing pressure, the effect on fishers of variations in stock status and availability, and their responses to those changes and those in management regimes \cite{Venables2009}. At the same time being simple enough to build and calibrate reliably with the available data. More comprehensive MSEs may also take the effects of the fishery on the broader environment, and economic and social effects into account \cite{Dichmont2008, Fulton2007}.

@@

@@

Using a MSE, the main objective of this work is to understand the fleet dynamics in a spatially and temporally heterogeneous mixed quota-regulated fishery when reducing from unmanaged (unconstrained catch quota) to MSY managed and to compare it with a situation where discards are allowed in order to assess on the biological and economic consequences. If LO and catch quotas are not fully enforced, there will be an incentive to continue discarding. Therefore, this manuscript tends to understand the likely adaptive change in fishing patterns that will help us to understand if this leads to a better balance between quotas and catches.

@@

\section{Methods}
\label{sec2}
The MSE approach is based upon a set of model of the "true" population dynamics of the species (called "operating model"; section \ref{sec2.1}). The operating model aims capturing the key processes in the dynamics of the fish population given the best knowledge available, and can be thought of as a minimum realistic model \cite{Punt1995}. The next step in the MSE is to simulate the process of monitoring the stock (called "observation model"; section \ref{sec2.2}). This resulted in simulated measurements such as individual harvester decision-making and the consequent biomass (including error). The observation data are then passed to the "management model" (section \ref{sec2.3}). The management model encompasses the harvest control rules (HCR). The HCR references to biological reference points (Fmsy) to produce management actions in the form of a harvest or effort level, changes in gear or spatial and temporal reallocations or restrictions of fishing effort. Management actions are rarely implemented without error. This error can come from two main sourrces: (i) resource users do not comply with the regulations, and (ii) the individual dynamics of resource users (e.g. when and where harvest is taken) are not accounted for in the HCR. By evaluating a range of HCRs against a set of plausible operating models using multiple performance metrics (section \ref{sec2.3}), MSE enables to study the different trade-offs involved with each management procedure.

@@

For purposes of model simplicity, we considered a hypothetical mixed fishery on two species. The fishery was modelled in a individual based dynamic state variable model. In order to allowed for fishing effort allocation, the model was seasonally and spatially explicit. The dynamics of the two fish species were governed by a simple age-structured model that is also seasonally and spatially explicit. In the age structured model for the fish species, individuals were assumed to be born at age 0, and in season 1. The number of fish of age $a$ at year $y$, in season $s$ and area $p$ was written as $N (a, y, s, p)$. The number of new-born individuals in the model was independent of the size of the adult population. Individuals could be born in each of the areas, such that  
\begin{equation}
N (0, y, 1, p) = R (p)
\end{equation}

Mortality in the model could occur from catches in the fishery, and natural causes such as predation, diseases, and scenesens. However, for simplicity we assumed that his natural mortality was negligible. Althought such absence of natural mortality impossible in reality, one could argue that the model thus mimics long-lived species. The decrease in population numbers was thus the result of the catches ($C (a, y, s, p)$), which were in turn a function of age dependent catchability $q(a)$, and fishing effort $E (y,s,p)$ in any time, season, and area. 
\begin{equation}
C (a, y, s, p) = q(a) * E(y,s,p),
\end{equation}
and 
\begin{equation}
N (a, y, s, p) = N (a, y, s, p) - C (a, y, s, p). 
\end{equation}

It was assumed that fishing mortality ocurred before migration ocurred. Migration for each species was defined by a matrix $Mig$ that defines the impact of migration (.e. immigration-emigration) on a given stock was also dependent on the relative sizes of the stocks. The size of that matrix  was defined by the number of age classes, seasons and number of immigrants into area $p$ ($im$) and emigrants leaving area $p$ ($em$) in the model. The migration in population numbers ($Mig (a, 1, s, im, em)$) was thus the proportion ($p (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs.   
\begin{equation}
Mig (a, 1, s, im, em) = Mig(a, 1, s, im, em) + N (a, y, s, em) * p (a, y, s, i, em, im),
\end{equation}
and then population numbers
\begin{equation}
N (a, y, s, im) = N (a, y, s, im) +  Mig (a, 1, s, im, em).
\end{equation}

Life history traits inputted were: (i)  during the first season, specie 1 spawned in $A$, while specie 2 spawned in $B$, (ii) every season, 20\% of specie 1 and 2 emigrated and immigrated between areas, (iii) growth following the von Berttalanffy equation (with the following parameters: $L\infty= 20$, $k= 0.093$), (iv) age-weight relationship ($W= L\infty*(1-e^{-k*a})$), (v) at the beginning of each year the fishing recruitment was stablish in 100.

The purpose of the operating model was not to reproduce the entire complexity of a real mixed fishery, but to defined plausible hypothesis about population dynamics and then to implemented the processes of interest, i.e., changes in population abundance, to finally measure the effect of the potential consequences associated with the fishers optimal choice location underlying assumption of the current state-dependat behaviour of individual fishing vessels.

@@

The maximum expected utility between current season $s$ and the end of the year was $V (C_i, Q_i, F_i, s)$, and the model started by setting $V (C_i, Q_i, F_i, s)= \Phi (C_i, Q_i, F_i)$. For preceding seasons, the expected utility depended on individual choices, and each time step individuals chose to visit fishing area $p$ (A, B and including area 0: “staying in port”), and to keep or discard any combination of the age classes caught of the quota species. This discarding was defined by a matrix $d$. The size of that matrix was defined by the number of species under quota constraints and the number of age classes. Each element could take the value 0 (discard) or 1 (keep on board and land). The expected utility for each state and each time step $s$ was calculated backward using stochastic dynamic programming \cite{ClarkandMangel2000}:
\begin{equation}
V (C_i, Q_i, F_i, s) = max_{p,d}( R(p, d, s)- G(p) - C(p) + E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1])),
\end{equation}
where $R(p, d, s)$ was the expected immediate contribution of the gross revenue from the sales of fish in a season resulting from choices $p$, and $d$ (gross revenues resulted from multiplying catches different age classes of species 1, species 2 and prices). Prices of fish were assumed to be dependant over fish age and time (subsection \ref{sec2.2.1}). $G(p)$ represented the incurred fuel costs per season from the choice of fishing area $a$, while  $ C(p)$ represented the variable operating costs (crew share, gear maintenance and landing costs, Table ~\ref{t:fishery}), which in turn depended on the change in cumulative landings and fish prices. The term $E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1]$ denoted the expected future utility taken over all possible states resulting from choices $p$, and $d$. The transition of these states were based on normal distributions of catch rates, using the means and variances for the species, as explained in the model conditioning section, following \cite{Poos2010}.

@@

If $U^*$ was the expected utility at the optimal choice for a given t, we set
\begin{equation}
\Delta_{p, d}(C_i, Q_i, F_i, s) =  U^* (C_i, Q_i, F_i, s) - U (C_i, Q_i, F_i, s),
\end{equation}
and then defined the probability of a choice for a given area and discarding as	
\begin{equation} \label{eq:solve}
P_{p, d}(C_i, Q_i, F_i, s) = \frac
                % Nominator
                {e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}}
                % Denominator
                {\sum_p \sum_d e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}},
\end{equation}
where $\sigma$ was a tuning parameter that measures how important was to be near optimal. A high value of sigma resulted in uniform probabilities of choices, and that vessels were distributed uniformly among the different fishing areas. In contrast, if sigma was small then all vessels concentrated in the optimal location (but note that $\sigma$ should be $> 0$). For computations, we used $\sigma = 40$ (noting that $\Delta$ ranged from 0 to $\sim 1.1 x 10^{11}$, but was generally of the order of $1.1 x 10^5$ in magnitude).

@@

\begin{table}[!h]
\centering
\caption{Fishery parameterization.}
\label{t:fishery}
\resizebox{0.7\textwidth}{!}{%
\begin{tabular}{@{}lc lc @{}} 
\hline
\textbf{model}                              &               & \textbf{Variable costs}                        &      \\\hline%&\textbf{Market value}&  \\ \hline
& & & \\%& & \\
number of vessels                           &700            &fuel costs (Euro day\textsuperscript{-1})       & 150  \\%& sp1 (Euro kg\textsuperscript{-1})                 & 1000 \\ 
$\sigma $                                   & 40            &gear maintenance (Euro day\textsuperscript{-1}) & 0   \\% & sp2 (Euro kg\textsuperscript{-1})                 & 1000   \\
number of areas                             & 2             &crew share                                      & 35\% \\%& & \\
number of seasons                           & 6             &landing costs (Euro t\textsuperscript{-1})      & 0    \\%& &\\
intial quota $Q_{sp1}$ and $Q_{sp2}$  & 200&                 &      \\%& & \\
& & & \\\hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependant pricing}
\label{sec2.2.1}
% Prices of fish have been assumed to be constant over fish age and time.
Common knowledge and case studies indicated that size and weight of a fish could be important attributes when determining its economic value. However, so far there has been no broader assessment whether the size-dependence of price really is prevalent and significant in fisheries. The results from \cite{Zimmermann2011, Zimmermann2013} underline that size-dependent pricing is common in Norwegian fisheries, and is therefore also of high relevance for decisions in fisheries management. Therefore, the resulting data of mean weights, average prices and total yield per weight classes and year were used for further analysis. We fitted linear mixed models (Bates and Maechler, 2010) and general additive models (Wood, 2010) in R (R: Development Core Team, 2012), using mean price and mean body weight as the response variable and covariate, respectively. Thus, the statistical models took the form  
\begin{equation}
 p_{i} \sim c_{0} + c_{1} w_{i} + f (y_{i}), 
\end{equation}
where p is price of observation i, wi is the mean weight of the corresponding weight class, and the term f(yi) corresponds to the effect of year, treated either as a random effect or as a smooth term. Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Size dependant pricing.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}lcccccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{6}{c}{season} \\ 
age                      & 1     & 2     & 3    & 4    & 5    & 6    \\ \hline
                      \\
1                       &    &    &   &   & & \\
2                       &    &    &   &   & &\\
3                       &    &    &   &   & &\\
4                       &    &    &   &   & &\\
\\
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l c c  c }
\hline
                                & \textbf{Scenario I}            & \textbf{Scenario II}                 & \textbf{Scenario III}           \\ 
                                & \textit{(landings selectivity)}  & \textit{(fulll avoidance of discards)} & \textit{(LO not fully enforced)} \\ \hline
& & &  \\
Discarding                      & Allowed                        & Not allowed                          & Ocurred but not perceived \\
Manager catch perception        & $C = L + D$                    &        $C = L$                       &  $C = L$  \\
Yield per recruitment model     & based in $F_L$                 &       based in $F_C$                 &  based in $F_L$  \\
Selectivity ($L/C$)             &  $ \neq 1$                     & $=1$                                 & $=1$\\
&  & &  \\\hline
\end{tabular}
}
\end{table}

@@

HCRs in the form of Quotas were determined endogenously by simple and relatively linear reduction in catch if fishing mortality exceeded Fmsy. This required that fishing mortality for each stock must not exceed Fmsy, which was a limit reference point. An Optimum Yield (OY) was determined based on a MSY that must prevented overfishing, and that could be reduced from the MSY limit to take into account social, economic and precautionary considerations.  Therefore, quota was determined by a set of harvest control rule parameters consisting of the exploitaion rate at MSY.

The resulted biomass harvested rate in a year $y$, depended in the manager catch perception and the standing biomass:
\begin{equation}
 H_{a, y, s} =\frac
                % Nominator
                {C_i numbers(a, y, s, p)}
                % Denominator
                {C_i numbers(a, y, s, p) \times B_i numbers(a, y, s, p)},
\end{equation}

\begin{equation}
 lratio (a, y, s) = \frac
                % Nominator
                {L_i numbers(a, y, s, p)}
                % Denominator
                {C_i numbers(a, y, s, p)},
\end{equation}

@@

\begin{equation}
 Q_{MSY} = \frac
                % Nominator
                {\sum( [\frac{H_{MSY}}{\bar{H}} \times H (a, s) \times lratio (a, s) \times B numbers(a, s)] \times wts) }
                % Denominator
                {number of vessels}, 
\end{equation}
\begin{equation}
 Q (y+1) = \max( \min(Q_{MSY}, Q(y) \times 1.15), Q(y) \times 0.85)), 
\end{equation}

@@

%- No quota constrained

%- Through a yield per recruit model, knowing growth, harvest rates and recruitment we can estimate how much to reduce the quota for achieving the MSY.  Since maximizing effort does not maximize catch, the question is if there is an optimum fishing rate that would lead to a maximum yield. The principal purpose of yield per recruit models is to get an idea of the effect of selection pattern and fishing mortality on the yield from a fixed number of individuals that enters the fishery.

%Therefore if we have a harvest rate of 0.32, we will need to reduce the harvest in a 68\%. Reduce quota in next run in 68\%. From this reduction in quota and the subsequent reduction in IQ, this scenario will be evaluated allowing and not allowing the fleet to discard.

@@

\newpage
%\begin{landscape}
Scenario I:
%----------------------------------------------------------------------------------------------------------------------------------------
\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_LO_disc_YieldLand.eps} 
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_LO_disc_YieldLand.eps} 
\end{minipage}
\caption{}
\end{figure}
%\end{landscape}

>>>>

\abstract{
TBD
We contrast three types of management plans to achieve maximum sustainable yields (MSY) from multiple stocks and compare their effectiveness based on a management strategy evaluation (MSE) that uses a dynamic state variable model including errors in decision-making in its operating model.}

@@

\keywords{management stategy evaluation; dynamics state variable model; errors in decision-making; landing obligation; maximum sustainable yield}

@@

@@

MSE involves building a simulation model for the entire process under study, complex enough both to address the current knowledge and uncertainty on the dynamics of fish stocks under fishing pressure, the effect on fishers of variations in stock status and availability, and their responses to those changes and those in management regimes \cite{Venables2009}. At the same time being simple enough to build and calibrate reliably with the available data. More comprehensive MSEs may also take the effects of the fishery on the broader environment, and economic and social effects into account \cite{Dichmont2008, Fulton2007}. In such modelling framework, advice and management systems can be quantitatively evaluated through simulation testing \cite{Kell2007, Dichmont2013}.

@@

Using a MSE, the main objective of this work is not to reproduce the entire complexity of a real mixed fishery, but to defined plausible hypothesis about population dynamics and then to implemented the processes of interest, i.e., changes in population abundance, to finally measure the effect of the potential consequences associated with the fishers optimal choice location underlying assumption of the current state-dependat behaviour of individual fishing vessels.to understand the fleet dynamics in a spatially and temporally heterogeneous mixed quota-regulated fishery when reducing from unmanaged (unconstrained catch quota) to MSY managed and to compare it with a situation where discards are allowed in order to assess on the biological and economic consequences. If LO and catch quotas are not fully enforced, there will be an incentive to continue discarding. Therefore, this manuscript tends to understand the likely adaptive change in fishing patterns that will help us to understand if this leads to a better balance between quotas and catches.

@@

\section{Methods}
\label{sec2}

The essential elements of the MSE framework that we followed is summarized in Figure \ref{fig:MSE}. The operating model (OM) aimed capturing the key processes in the dynamics of the fish population given the best knowledge available, and can be thought of as a minimum realistic model \cite{Punt1995}. The OM was built using a set of models of the dynamics of fish stocks under fishing pressure and coupled with the effect on fishers of variations in stock status and availability (sections \ref{sec2.1} and \ref{sec2.2} respectively). This resulted in simulated measurements (called "observation model") such as individual harvester decision-making (including error) and the consequent biomass of fish stocks, including the essential elements for calculating the individual harvester economic performance. The observation data were then passed to the "management model" (section \ref{sec2.3}). The management model encompassed the harvest control rules (HCR). The HCR referenced to biological reference points (Fmsy) to produce management actions in the form of a harvest or effort level: changes in selectivity or spatial and temporal reallocations or restrictions of fishing effort. Costs and benefits, both economic and in terms of risks to both stock and livelihoods, could be computed and compared across different scenarios and management procedures (section \ref{sec2.3}).

% Management actions are rarely implemented without error. This error can come from two main sourrces: (i) resource users do not comply with the regulations, and (ii) the individual dynamics of resource users (e.g. when and where harvest is taken) are not accounted for in the HCR. By evaluating a range of HCRs against a set of plausible operating models using multiple performance metrics (section \ref{sec2.3}), MSE enables to study the different trade-offs involved with each management procedure.

\begin{figure}[!h]
\centering
\includegraphics[width=0.7\textwidth]{Figures/MSE_6.eps} 
\caption{The conceptual framework and how it was mapped.}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=0.6\textwidth]{Figures/Areadynamics3.eps} 
\caption{The conceptual framework and how it was mapped.}
\label{fig:MSE}
\end{figure}

@@

For purposes of model simplicity, we considered a hypothetical mixed fishery on two species. The fishery was modelled in a individual based dynamic state variable model. In order to allowed for fishing effort allocation, the model was seasonally (6 seasons) and spatially (areas A and B) explicit. The dynamics of the two fish species were governed by a simple age-structured model that is also seasonally and spatially explicit. The age structured model for the fish species was based on 4 cohorts, and individuals were assumed to be born at age 0, and in season 1. The number of fish $i$ of age $a$ at year $y$, in season $s$ and area $p$ was written as $N_i (a, y, s, p)$. The number of new-born individuals in the model was independent of the size of the adult population, but was function of area $p$ ($R_i (p)$). Numbers of recruits were set to 100 individuals during the first season, and spawning population of species 1 ocurred in area $A$, while species 2 did so in area B. Thus, individuals could be born in each of the areas, such that:  
\begin{equation}
N_i (0, y, 1, p) = R_i (p)
\end{equation}

Moreover, combining the weight-based von Bertalanffy growth equation ($L\infty= 20$, $k= 0.093$), with the age-weight relationship ($W= L\infty*(1-e^{-k*a})$); weight per fish was higher for the older fish. Mortality in the model could occur from catches in the fishery, and natural causes such as predation, diseases, and scenesens. However, for simplicity we assumed that his natural mortality was negligible. Althought such absence of natural mortality impossible in reality, one could argue that the model thus mimics long-lived species. The decrease in population numbers was thus the result of the catches ($C_i (a, y, s, p)$), which were in turn a function of age dependent catchability $q(a)$, and fishing effort $E (y,s,p)$ in any time, season, and area. 
\begin{equation}
C_i (a, y, s, p) = q(a) * E(y,s,p),
\end{equation}
and 
\begin{equation}
N_i (a, y, s, p) = N_i (a, y, s, p) - C (a, y, s, p). 
\end{equation}

It was assumed that fishing mortality ocurred before migration ocurred. Migration for each species was defined by a matrix $Mig$ that defines the impact of migration (.e. immigration-emigration) on a given stock was also dependent on the relative sizes of the stocks. The size of that matrix  was defined by the number of age classes, seasons and number of immigrants into area $p$ ($im$) and emigrants leaving area $p$ ($em$) in the model. A 20 \% constant migration during any season was set between areas. The migration in population numbers ($Mig (a, 1, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs.   
\begin{equation}
Mig (a, 1, s, im, em) = Mig(a, 1, s, im, em) + N (a, y, s, em) * P (a, y, s, i, em, im),
\end{equation}
and then population numbers
\begin{equation}
N (a, y, s, im) = N (a, y, s, im) +  Mig (a, 1, s, im, em).
\end{equation}

@@

The maximum expected utility between current season $s$ and the end of the year was $V (C_i, Q_i, F_i, s)$, and the model started by setting $V (C_i, Q_i, F_i, s)= \Phi (C_i, Q_i, F_i)$. For preceding seasons, the expected utility depended on individual choices, and each time step individuals chose to visit fishing area $p$ (A, B and including area 0: “staying in port”), and to keep or discard any combination of the age classes caught of the quota species. This discarding was defined by a matrix $d$. The size of that matrix was defined by the number of species under quota constraints and the number of age classes. Each element could take the value 0 (discard) or 1 (keep on board and land). The expected utility for each state and each time step $s$ was calculated backward using stochastic dynamic programming \cite{ClarkandMangel2000}:
\begin{equation}
V (C_i, Q_i, F_i, s) = max_{p,d}( R(p, d, s)- G(p) - C(p) + E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1])),
\end{equation}
where $R(p, d, s)$ was the expected immediate contribution of the gross revenue from the sales of fish in a season resulting from choices $p$, and $d$ (gross revenues resulted from multiplying catches different age classes of species 1, species 2 and prices). Prices of fish were assumed to be dependant over fish age (subsection \ref{sec2.2.1}). $G(p)$ represented the incurred fuel costs per season from the choice of fishing area $a$, while  $ C(p)$ represented the variable operating costs (crew share, gear maintenance and landing costs, Table ~\ref{t:fishery}), which in turn depended on the change in cumulative landings and fish prices. The term $E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1]$ denoted the expected future utility taken over all possible states resulting from choices $p$, and $d$. The transition of these states were based on normal distributions of catch rates, using the means and variances for the species, as explained in the model conditioning section, following \cite{Poos2010}.

@@

If $U^*$ was the expected utility at the optimal choice for a given t, we set
\begin{equation}
\Delta_{p, d}(C_i, Q_i, F_i, s) =  U^* (C_i, Q_i, F_i, s) - U (C_i, Q_i, F_i, s),
\end{equation}
and then defined the probability of a choice for a given area and discarding as	
\begin{equation} \label{eq:solve}
P_{p, d}(C_i, Q_i, F_i, s) = \frac
                % Nominator
                {e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}}
                % Denominator
                {\sum_p \sum_d e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}},
\end{equation}
where $\sigma$ was a tuning parameter that measures how important was to be near optimal. A high value of sigma resulted in uniform probabilities of choices, and that vessels were distributed uniformly among the different fishing areas. In contrast, if sigma was small then all vessels concentrated in the optimal location (but note that $\sigma$ should be $> 0$). For computations, we used $\sigma = 40$ (noting that $\Delta$ ranged from 0 to $\sim 2 x 10^{3}$, but was generally of the order of $1 x 10^2$ in magnitude).

@@

\begin{table}[!h]
\centering
\caption{Model and fishery conditioning.}
\label{t:fishery}
\resizebox{0.9\textwidth}{!}{%
\begin{tabular}{@{}lc lc lc @{}} 
\hline
\textbf{model}                              &               & \textbf{Fishery variable costs}                &      &\textbf{Fishery }&  \\ \hline
& & & \\%& & \\
number of vessels                           &700            &fuel costs (Euro day\textsuperscript{-1})       & 150  & q                 & 0.0005 \\ 
$\sigma $                                   & 40            &gear maintenance (Euro day\textsuperscript{-1}) & 0    & effort (p,s)      & 1   \\
number of areas                             & 2             &crew share                                      & 35\% & CPUE & mean($pop*q*wts(yy-2:yy)$)\\
number of seasons                           & 6             &landing costs (Euro t\textsuperscript{-1})      & 0    & CPUE dev& $0.08*CPUE$\\
intial quota $Q_{sp1}$ and $Q_{sp2}$  & 200&                 &      \\%& & \\
& & & \\\hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependant pricing}
\label{sec2.2.1}
Prices of fish have been assumed to be fixed over time but influenced by the size of the catch. Common knowledge and case studies indicate that size and weight of a fish could be important attributes when determining its economic value \cite{Zimmermann2011, Zimmermann2013}. Therefore, the resulting data of mean weights and average prices were used for further analysis. We fitted linear mixed models, using mean price and mean body weight as the response variable and covariate, respectively. Thus, following \cite{Zimmermann2011}, the statistical models took the form:  
\begin{equation}
 pw_{i} \sim p_i \bar{w_i} + \beta_0 \times \frac{w_i-\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p$ is the mean price of species $i$, $\bar{w_i}$ is the mean weight of the corresponding weight classes, and the fraction corresponded to the standarization of the mass relative to the mean observed individual catch mass over all ages classes. $\beta_0$ gave the price increase when individial mass was increased by $\bar{w}$. We used mean prices of 150 Euro kg\textsuperscript{-1} for both species.
 %Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Linear mass-prices estimated based on mean prices per mass age-classes. The price slopes $\beta_0$ were assumed to be similar to mean prices.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}lcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
                         & 1     & 2     & 3    & 4   \\ \hline
                      \\
species 1                &  778  & 1354   & 1780  & 2096  \\
species 2                &  778  & 1354   & 1780  & 2096  \\
\\
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l c c  c }
\hline
                                & \textbf{Scenario I}            & \textbf{Scenario II}                 & \textbf{Scenario III}           \\ 
                                & \textit{(landings selectivity)}& \textit{(fulll avoidance of discards)} & \textit{(LO not fully enforced)} \\ \hline
& & &  \\
Discarding                      & Allowed                        & Not allowed                          & Ocurred but not perceived \\
Manager catch perception        & $C = L + D$                    &        $C = L$ ($D = 0$)                      &  $C = L$ ($D \neq 0$) \\
Selectivity ($l_{ratio}$)         &  $ \neq 1$                     & $=1$                                 & $=1$\\
Yield per recruitment model     & based in $F_L$                 &       based in $F_C$                 &  based in $F_L$  \\

&  & &  \\\hline
\end{tabular}
}
\end{table}

@@

HCRs in the form of quotas were determined endogenously by simple and relatively linear reduction in catch if fishing mortality exceeded Fmsy. This required that fishing mortality for each stock must not exceed Fmsy, which was a limit reference point. An Optimum Yield (OY) was determined based on a MSY that must prevented overfishing, and that could be reduced from the MSY limit to take into account social, economic and precautionary considerations.  Therefore, quota was determined by a set of harvest control rule parameters consisting of the exploitaion rate at MSY.

The resulted biomass harvested rate in a year $y$, depended in the manager catch perception (based in Table ~\ref{t:fishery}) and the standing biomass:
\begin{equation}
 H_{a, y, s} =\frac
                % Nominator
                {C_{i (numbers)}(a, y, s, p)}
                % Denominator
                {C_{i (numbers)}(a, y, s, p) \times B_{i (numbers)}(a, y, s, p)},
\end{equation}

\begin{equation}
 l_{ratio} (a, y, s) = \frac
                % Nominator
                {L_{i (numbers)}(a, y, s, p)}
                % Denominator
                {C_{i (numbers)}(a, y, s, p)},
\end{equation}

Through a yield per recruitment model, knowing growth, harvest rates and recruitment we can estimate how much to reduce the quota for achieving the MSY.

@@

\begin{equation}
 Q_{MSY} = \frac
                % Nominator
                {\sum( [\frac{H_{MSY}}{\bar{H}} \times H (a, s) \times l_{ratio} (a, s) \times B_{(numbers)}(a, s)] \times wts) }
                % Denominator
                {number\  of\  vessels}, 
\end{equation}
\begin{equation}
 Q (y+1) = \max( \min(Q_{MSY}, Q(y) \times 1.15), Q(y) \times 0.85), 
\end{equation}

@@

@@

\newpage
%\begin{landscape}
Scenario I:
%----------------------------------------------------------------------------------------------------------------------------------------
\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_LO_disc_YieldLand1.eps} 
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_LO_disc_YieldLand1.eps} 
\end{minipage}
\caption{}
\end{figure}
%\end{landscape}
